Methods

### 2024-04-05 Sections/Intro.qmd
more toc test
toc update
toc
tweak
turn off external

>>>>

---
code-fold: true
code-tools: true
toc: true
toc-location: body
toc-title: Contents
---

[Link to HTW project page](https://tegorman13.github.io/htw/){target="_blank"}\

[Working Draft of HTW Manuscript](https://tegorman13.github.io/htw/paper.html){target="_blank"}

[repo](https://github.com/tegorman13/htw){target="_blank"} \

_______________________________________________________________________________
